---
title: "FARS"
author: "Oluwaseun Gakenou"
date: "2020-08-08"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r global_options}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(fars)
```

To read files or path from the system into the package. Error occurs if filename does not exist
```{r}
library(readr)
library(dplyr)

fars_read("accident_2013.csv")
```

To create filename for a particular year
```{r}
filename<- make_filename(2013)
```

In order to create a dataframe containing list of years and month from the file imported
PS: returns NULL if year is invalid
```{r}
fars_read_years(as.list(2000, 2001, 2002))
```

In order to reduce data to a yearly time step
```{r}
 fars_summarize_years(c(2013, 2014, 2015, 2018))
```

In order to create a map plotted with latitude and longitude for different state per year using unique state number
Ps: error occurs if state number is invalid and returns NULL if state number == 0
```{r}
  fars_map_state(12, 2013)
```
