---
title: "FARS"
author: "Oluwaseun Gakenou"
date: "2020-08-08"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Packages to be loaded
```{r global_options}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(fars)
library(dplyr)
library(tidyr)
library(magrittr)
library(maps)
library(graphics)
library(readr)
library(tibble)
```

To read files or path from the system into the package. Error occurs if filename does not exist

accident_2013 <- system.file("extdata", "accident_2013.csv", package = "fars")

usage: fars_read(filename = accident_2013)



To create filename for a particular year

usage: make_filename(2013)



In order to create a dataframe containing list of years and month from the file imported
PS: returns NULL if year is invalid

usage: fars_read_years(years = c(2013,2014,2015))



In order to reduce data to a yearly time step
library(dplyr)

usage: fars_summarize_years(years = c(2013,2014,2015))



In order to create a map plotted with latitude and longitude for different state per year using unique state number
Ps: error occurs if state number is invalid and returns NULL if state number == 0

usage: fars_map_state(6, 2013)
